MCTS Based on Simple Regret

### 2012-02-22 slides/slides.tex
heuristic sampling schemes

{\bf M}onte {\bf C}arlo {\bf T}ree {\bf S}earch helps in large search spaces.
\begin{itemize}
\item Starts with the root only.
\item Repeats:
  \begin{enumerate}
    \item \textbf{Selection:} select a branch to explore.
    \item \textbf{Expansion:} adds children of the leaf to the stored
      tree.
    \item \textbf{Simulation:} continues search (using a simple
      strategy) until a goal state is reached.
    \item \textbf{Backpropagation:} values of each stored node 
      are updated.
  \end{enumerate}
\end{itemize}
\textbf{Adaptive} MCTS samples `good' moves more frequently,\\
but sometimes {\bf explores} new directions.
\end{frame}

@@

>>>>

{\bf M}onte {\bf C}arlo {\bf T}ree {\bf S}earch helps in large search spaces.
\begin{itemize}
\item<+-> Starts with the root only.
\item<+-> Repeats:
  \begin{enumerate}
    \item \textbf{Selection:} select a branch to explore.
    \item<+-> \textbf{Expansion:} adds children of the leaf to the stored
      tree.
    \item<+-> \textbf{Simulation:} continues search (using a simple
      strategy) until a goal state is reached.
    \item<+-> \textbf{Backpropagation:} values of each stored node 
      are updated.
  \end{enumerate}
\end{itemize}
\vspace{1em}
\textbf{Adaptive} MCTS samples `good' moves more frequently,\\
but sometimes {\bf explores} new directions.
\end{frame}

@@

\begin{frame}{Heuristic sampling schemes}

\onslide<+->
$\varepsilon$-greedy:
\begin{itemize} 
\item Pulls the empirically best arm with probability $\varepsilon$.
\item Any other arm with probability $\frac {1-epsilon} {K-1}$.
\item Exhibits exponentially decreasing simple regret.
\item Uniform sampling when $\varepsilon=\frac 1 K$, much better when
  $\varepsilon=\frac 1 2$.
\end{itemize}
\vspace{1em}
\onslide<+->
$UCB_{\sqrt{\cdot}}$ ($\sqrt{\cdot}$ instead of $\log$): 
\begin{itemize}
\item Pulls arm $i$ that maximizes
  $b_i=\overline X_i+\sqrt {\frac {c \sqrt n} {n_i}}$. 
\item Exhibits superpolynomially decreasing simple regret.
\end{itemize}
\end{frame}
